Efficient Coalition Formation for Web Services

### 2013-04-22 papers/coalition/SCC2013_WSCoalition.tex
Changes

When dealing with cooperative games, two issues need to be
addressed:\\ 1. What coalition to form (Canonical games)? \\
2. How to reward each member when a task is completed
(Coalition-formation games)?\\
%
The following definitions help address these two issues.

@@

Figure \ref{performanceall} depicts the results of optimal
\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
in \emph{one grand community with many web services} scenario. For
\emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally 
intractable and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and \emph{3-Way Satisfaction} are also performing well.

@@

As mentioned in Section \ref{s:preliminaries}, the concept of
\emph{core}, assumes no coalition of players can gain anything by
deviating, which is a fairly strong requirement, and that is why
the notion of \emph{$\epsilon$-core} was introduced. Least-Core
$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
the core is not empty. We evaluated the non-emptiness of \emph{$\epsilon$-core} set using the
valuation function and a set of web services. We picked random
number of web services from the dataset and formed around 10,000
random coalitions consisting of 3 to 26 web services. We choose 26
as the maximum number of members in our coalition since it
is computationally very complex for larger coalitions to verify whether 
\emph{$\epsilon$-core} set is empty or not. Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$.v(C)} by deviating. We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non emptiness. The results in Figure
\ref{f_leastcore} illustrates that almost 10\% of our random web
service coalitions have non-empty \emph{core} solution and
\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
let agents gain only 30\% more of $v(C)$ by deviating.

>>>>

When dealing with cooperative games, two issues need to be
addressed:\\ 1. What coalitions to form? \\
2. How to reward each member when a task is completed?\\
%
The following definitions help address these two issues.

@@

Figure \ref{performanceall} depicts the results of optimal
\emph{$\epsilon$-core}, \emph{Depth-1 Convex-Checker},
\emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfaction}
\cite{DBLP:conf/IEEEscc/LimTMB12}, and \emph{2 Player
Non-Cooperative} \cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods
in \emph{one grand community with many web services} scenario. For
\emph{$\epsilon$-core}, we assign $\epsilon$ to 15\% of total
community worth, $\epsilon = 0.15 \times v(C)$, which allows
subsets of the coalition to gain maximum 15\% of $v(C)$. In the
\emph{optimal $\epsilon$-core} method, we capped the coalition
size to 25 web services, since the method is computationally 
intractable and anything more than that would make it
impractical to run in our simulations. In the other methods, there
were no cap on size of the community and we had communities of
size 60 web services at some points. The results show that our
\emph{depth-2 convex checker} method is performing better compared
to the other methods and its performance is close to optimal
\emph{$\epsilon$-core} method. Our \emph{depth-1 convex checker}
and the \emph{3-Way Satisfaction} method, are also performing well.

@@

As mentioned in Section \ref{s:preliminaries}, the concept of
\emph{core}, assumes no coalition of players can gain anything by
deviating, which is a fairly strong requirement, and that is why
the notion of \emph{$\epsilon$-core} was introduced. Least-Core
$e(G)$ of a game $G$, is the minimum amount of $\epsilon$ so that
the core is not empty. We evaluated the non-emptiness of \emph{$\epsilon$-core} set using the
valuation function and a set of web services. We picked random
number of web services from the dataset and formed around 10,000
random coalitions consisting of 3 to 26 web services. We choose 26
as the maximum number of members in our coalition since it
is computationally very complex for larger coalitions to verify whether 
\emph{$\epsilon$-core} set is empty or not. Also instead of considering $\epsilon$ amount of constant deviation in \emph{$\epsilon$-core} definition (Equation \ref{eq:core}), we similarly defined \emph{relative $\epsilon$-core} concept where no coalition would benefit more than \emph{$\epsilon$ $\times$ v(C)} by deviating. We set $\epsilon$ between 0 and 1 and verify the \emph{relative $\epsilon$-core} set non-emptiness. The results in Figure
\ref{f_leastcore} illustrates that almost 10\% of our random web
service coalitions have non-empty \emph{core} solution and
\emph{$\epsilon$-core} solution is \emph{always} non-empty when we
let agents gain only 30\% more of $v(C)$ by deviating.
